---
title: "DSC_1105_FA2"
author: "Frances Aneth Rosales"
date: "`r Sys.Date()`"
output:
  html_document:
    css: FA2.css
---
<style>
  body {
    text-align: justify;
  }
</style>


<br>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br><br><br><br>

# Read & Show Data


```{r}

library(readr)
filepath <- read_csv("cytof_one_experiment.csv")
head(filepath)
```
<span style="color: purple;"> <h1> <li> 1 Using <b> pivot_longer </b> </li> </h1> </span>

```{r pivot_longer}

library(dplyr)
library(tidyr)

reshaped_data <- filepath %>%
  pivot_longer(cols = everything(), 
               names_to = "Protein Identity", 
               values_to = "Amount")

print(reshaped_data[, c("Protein Identity", "Amount")])




```
<br><br>

# Number of ROWS

```{r pivot_longer_ROw}

library(dplyr)
library(tidyr)

reshaped_data <- filepath %>%
  pivot_longer(cols = everything(), 
               names_to = "Protein Identity", 
               values_to = "Amount")

print(nrow(reshaped_data))



```



<br><br><br><br>

<span style="color: purple;">  <h1> <li> 2 Using <b> group_by </b> </li> </h1> </span>


```{r group_by}
library(dplyr)
groupby_function <- reshaped_data %>%
  group_by(`Protein Identity`) %>%
  summarise(
    Median = median(Amount),
    MAD = mad(Amount)
  )

```

<br>

<h1> <b> TABLE OF MEDIAN & MAD </b> </h1> 

```{r group_by_html}
library(magrittr)
library(kableExtra)


kable(groupby_function, "html") %>%
  kable_styling()
```

<br><br><br><br>

<span style="color: purple;">  <h1> <b>  3 Spread-Location (s-l) Plot </b> </h1> 

</span>

```{r plott}
library(ggplot2)
ggplot(groupby_function, aes(x = MAD, y = Median)) +
  geom_point() +
  labs(title = "Spread-Location (s-l) Plot",
       x = "Median Absolute Deviation (MAD)",
       y = "Median Protein Level (MPL) ")


```

<h1> <b> <li> Interpretation </li> </b> </h1> 

<h3> The relationship between the median absolute deviation (MAD) and the median protein level is shown in the spread-location (s-l) plot. The data exhibits a stable degree of variability, with the majority of observations being centered around a particular median value. A steady, predictable distribution of protein levels with few outliers is shown by the s-l plot. This plot offers important insights into the characteristics of the protein data by assisting in the identification of trends and possible outliers. </h3>


<br><br><br><br><br>



<span style="color: purple;">  <h1> <b> 4 The example_gymnastics_2 DATA: </b> </h1> </span>


```{r dcldat}

library(dcldata)
library(tidyverse)

data(example_gymnastics_2)

exampl_func  = example_gymnastics_2 %>%
  pivot_longer(cols = -country, 
               names_to = "event_year", 
               values_to = "Score") %>%
  separate(event_year, into = c("Event", "Year"), sep = "_", convert = TRUE)

```

<br>
 
Click to Hide/Show Data

<button onclick="hideoutput()" style="background: #e8ccd7;"> 
HIDE/SHOW
</button>
<div id="codeinputhere4" style="display:block;">


<h1> <b> TABLE OF GYMNASTICS_2 </b> </h1> 
```{r dcldat_table}
library(magrittr)
library(kableExtra)


kable(exampl_func, "html") %>%
  kable_styling()
```

</div>
<script>
function hideoutput() {
  var x = document.getElementById("codeinputhere4");
  if (x.style.display === "block") {
    x.style.display = "none";
    
    
  } else {
    x.style.display = "block";
  }
}
</script>